PANCHANGE_data_preprocessing

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added source chunk for data path and amended data chunks

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette=COPINGpalette2
```

@@

## GLAD demographics
# Read in data
```{r glad dem cols}
glad.dem.raw <- readRDS(file = "../data_raw/glad/dem_glad.rds")
dim(glad.dem.raw)
colnames(glad.dem.raw)
```

@@

```{r glad gad cols}
glad.gad.raw <- readRDS(file = "../data_raw/glad/gad_glad.rds")
dim(glad.gad.raw)
colnames(glad.gad.raw)
```

@@

```{r glad mhq cols}
glad.mhq.raw <- readRDS(file = "../data_raw/glad/mhq_glad.rds")
dim(glad.mhq.raw)
colnames(glad.mhq.raw)
```

@@

```{r glad pcl cols}
glad.pcl.raw <- readRDS(file = "../data_raw/glad/pcl_glad.rds")
dim(glad.pcl.raw)
colnames(glad.pcl.raw)
```

@@

```{r glad phq cols}
glad.phq.raw <- readRDS(file = "../data_raw/glad/phq_glad.rds")
dim(glad.phq.raw)
colnames(glad.phq.raw)
```

@@

```{r coping glad gad cols}
coping.glad.gad.raw <- readRDS(file = "../data_raw/coping_glad/gad_coping_glad.rds")
dim(coping.glad.gad.raw)
colnames(coping.glad.gad.raw)
```

@@

```{r coping glad pcl cols}
coping.glad.pcl.raw <- readRDS(file = "../data_raw/coping_glad/pcl_coping_glad.rds")
dim(coping.glad.pcl.raw)
colnames(coping.glad.pcl.raw)
```

@@

```{r coping glad phq cols}
coping.glad.phq.raw <- readRDS(file = "../data_raw/coping_glad/phq_coping_glad.rds")
dim(coping.glad.phq.raw)
colnames(coping.glad.phq.raw)
```

>>>>

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette = COPINGpalette2
```

@@

# Source data file paths

```{r source file path}
#source raw data directory: data.raw_path
source("../PANCHANGE_raw_path.R")
```

## GLAD demographics
# Read in data
```{r glad dem cols}
glad.dem.raw <- readRDS(file = paste0(data.raw_path, "/glad/dem_glad.rds"))
dim(glad.dem.raw)
colnames(glad.dem.raw)
```

@@

```{r glad gad cols}
glad.gad.raw <- readRDS(file = paste0(data.raw_path, "/glad/gad_glad.rds"))
dim(glad.gad.raw)
colnames(glad.gad.raw)
```

@@

```{r glad mhq cols}
glad.mhq.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhq_glad.rds"))
dim(glad.mhq.raw)
colnames(glad.mhq.raw)
```

@@

```{r glad pcl cols}
glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_glad.rds"))
dim(glad.pcl.raw)
colnames(glad.pcl.raw)
```

@@

```{r glad phq cols}
glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_glad.rds"))
dim(glad.phq.raw)
colnames(glad.phq.raw)
```

@@

```{r coping glad gad cols}
coping.glad.gad.raw <- readRDS(file = paste0(data.raw_path,"/coping_glad/gad_coping_glad.rds"))
dim(coping.glad.gad.raw)
colnames(coping.glad.gad.raw)
```

@@

```{r coping glad pcl cols}
coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/coping_glad/pcl_coping_glad.rds"))
dim(coping.glad.pcl.raw)
colnames(coping.glad.pcl.raw)
```

@@

```{r coping glad phq cols}
coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/coping_glad/phq_coping_glad.rds"))
dim(coping.glad.phq.raw)
colnames(coping.glad.phq.raw)
```
